Enrich the datasets with new columns.

### 2020-08-26 inst/analysis/enrich_dataset.Rmd

source("inc/paths.R")
source("insights.R", local = knitr::knit_global())
source("preprocess.R", local = knitr::knit_global())
```

@@

@@

```{r separate_datasets}
eval_calls_core <- eval_calls %>% filter(eval_source_type == "core")
eval_calls_packages <- eval_calls %>% filter(eval_source_type %in% c("package", "<undefined>") )
eval_calls_kaggle <- eval_calls %>% filter(eval_source_type == "kaggle")
```

@@

```{r}
eval_calls_raw <- eval_calls_raw %>% select(-ends_with("_type")) %>% left_join(eval_calls)
```

```{r write_back}
write_fst(eval_calls, EVALS_RAW_FILE)

@@

Notebook execution was `r difftime(Sys.time(), now)`.

>>>>

source("inc/paths.R")
source("inc/latextags.R")
source("inc/setup.R")
theme_set(theme_minimal())
create_tags(path(TAGS_DIR, "enrichDataset.tex"), prefix="", default=TRUE)

source("insights.R", local = knitr::knit_global())
source("preprocess.R", local = knitr::knit_global())
```

@@

```{r shrink_to_corpus}
corpus_files <- read_lines(CORPUS_FILE)
eval_calls <- eval_calls %>% keep_only_corpus(corpus_files)
```

```{r fake_srcref}
eval_calls <- eval_calls %>% add_fake_srcref()
```

@@

```{r separate_datasets}
eval_calls_core <- eval_calls %>% filter(eval_source_type == "core")
eval_calls_packages <- eval_calls %>% filter(eval_source_type == "package" )
eval_calls_kaggle <- eval_calls %>% filter(eval_source_type == "kaggle")
```

@@

```{r}
#eval_calls_raw <- eval_calls_raw %>% select(-ends_with("_type")) %>% left_join(eval_calls)

```

# Unknown evals

Some `eval` do not have srcref information attached and are not in *base*. It is often because they are located in a function that is created by another function.

```{r unknown_evals}

nb_eval_calls <- count(eval_calls, wt = nb_ev_calls)$n

undefined_evals <- eval_calls %>% filter(eval_source_type == "<undefined>")

nb_undefined <- undefined_evals %>% count(wt = nb_ev_calls)

nb_different_call_expr <- undefined_evals %>% select(eval_call_expression) %>% n_distinct()

r("undefined evals", nb_undefined$n)
r("percent undefined eval", ratio(nb_undefined$n, nb_eval_calls))
r("undefined eval expressions", nb_different_call_expr)
```

How many different undefined eval call sites do we have per package run?

```{r undefined_per_package}
undefined_per_package <- undefined_evals %>% group_by(package) %>% summarize(n = n_distinct(eval_call_expression)) 
known_packages <- setdiff(eval_calls$package, undefined_per_package$package) %>% as_tibble_col(column_name = "package")
known_packages <- known_packages %>% mutate(n = 0)

undefined_per_package <- bind_rows(undefined_per_package, known_packages) %>% arrange(desc(n))

```

# Write

```{r write_back}
write_fst(undefined_per_package, PACKAGE_EVALS_DYNAMIC_FILE)

write_fst(eval_calls, EVALS_RAW_FILE)

@@

```{r}
duration <- difftime(Sys.time(), now)
```

Notebook execution was `r duration` `r units(duration)`.
